Northern Pikeminnow Predation on Juvenile Chinook Salmon and Potential Impacts to Local Populations

### 2021-12-13 analysis/paper/paper.Rmd
converted some single digit numbers to english

```{r load-libraries}
library(tidyverse)
library(magrittr)
library(lubridate)
library(tidytable)
library(janitor)
library(purrr)
library(here)
library(FSA)
library(knitr)
library(kableExtra)
library(stringi)

@@

We caught `r prettyNum(total_cpue[total_cpue$event_name == "Fall 2019", "n_fish"])` and `r prettyNum(total_cpue[total_cpue$event_name == "Fall 2020", "n_fish"])` Northern Pikeminnow during Fall 2019 and Fall 2020, respectively. The catch per unit effort, measured as number of Northern Pikeminnow captured per angler hour, for each was `r prettyNum(total_cpue[total_cpue$event_name == "Fall 2019", "catch_per_hr"], digits = 3)` for Fall 2019 and `r prettyNum(total_cpue[total_cpue$event_name == "Fall 2020", "catch_per_hr"], digits = 3)` for Fall 2020 (Figure \@ref(fig:cpue-fig)). During Fall 2019 we had a total of `r sum(N_mods[[3]][[1]]$m)` recaptures which included `r LP_mod[[3]][[1]]$m` unique individuals i.e. `r sum(N_mods[[3]][[1]]$m) - LP_mod[[3]][[1]]$m` was captured more than once. There were `r sum(N_mods[[3]][[3]]$m)` recaptures in Fall 2020 which included `r LP_mod[[3]][[3]]$m` unique individuals. Summaries of parameters for both the single-census and multiple-census mark-recapture estimators are provided in Table \@ref(tab:abund-data-lp) and Table \@ref(tab:abund-data-schn), respectively.

>>>>

```{r load-libraries}
library(tidyverse)
library(magrittr)
library(lubridate)
library(tidytable)
library(janitor)
library(purrr)
library(here)
library(FSA)
library(knitr)
library(kableExtra)
library(stringi)
library(english)

@@

We caught `r prettyNum(total_cpue[total_cpue$event_name == "Fall 2019", "n_fish"])` and `r prettyNum(total_cpue[total_cpue$event_name == "Fall 2020", "n_fish"])` Northern Pikeminnow during Fall 2019 and Fall 2020, respectively. The catch per unit effort, measured as number of Northern Pikeminnow captured per angler hour, for each was `r prettyNum(total_cpue[total_cpue$event_name == "Fall 2019", "catch_per_hr"], digits = 3)` for Fall 2019 and `r prettyNum(total_cpue[total_cpue$event_name == "Fall 2020", "catch_per_hr"], digits = 3)` for Fall 2020 (Figure \@ref(fig:cpue-fig)). During Fall 2019 we had a total of `r as.english(sum(N_mods[[3]][[1]]$m))` recaptures which included `r as.english(LP_mod[[3]][[1]]$m)` unique individuals i.e. `r as.english(sum(N_mods[[3]][[1]]$m) - LP_mod[[3]][[1]]$m)` was captured more than once. There were `r as.english(sum(N_mods[[3]][[3]]$m))` recaptures in Fall 2020 which included `r as.english(LP_mod[[3]][[3]]$m)` unique individuals. Summaries of parameters for both the single-census and multiple-census mark-recapture estimators are provided in Table \@ref(tab:abund-data-lp) and Table \@ref(tab:abund-data-schn), respectively.
